Meta-analysis on sex in MSSM-Penn-Pitt and HBCC ACC/DLPFC

### 2020-08-01 individual-cohorts/meta-analysis.Rmd
preserve rownames

```{r store}
# Code
CODE <- Folder(name = "Meta-analysis on sex", parentId = parentId)
CODE <- synStore(CODE)

# Store meta-analysis
res_dlpfc %>%
  write.table(file = 'CMC_dlpfc_Sex_meta_analysis.tsv', sep = '\t', row.names=F, quote=F)
nEXP_OBJ = File('CMC_dlpfc_Sex_meta_analysis.tsv', 
                name = 'Sex Normalised, meta-analysis (DLPFC)', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)
res_acc %>%
  write.table(file = 'CMC_acc_Sex_meta_analysis.tsv', sep = '\t', row.names=F, quote=F)
nEXP_OBJ = File('CMC_acc_Sex_meta_analysis.tsv', 
                name = 'Sex Normalised, meta-analysis (ACC)', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)
```

>>>>

```{r store}
# Code
CODE <- Folder(name = "Meta-analysis on sex", parentId = "syn22276904") # Make sure these match the folder name and parent Id in the first chunk.
CODE <- synStore(CODE)

# Store meta-analysis
res_dlpfc %>%
  tibble::rownames_to_column(var = "gene_id") %>% 
  write.table(file = 'CMC_dlpfc_Sex_meta_analysis.tsv', sep = '\t', row.names=F, quote=F)
nEXP_OBJ = File('CMC_dlpfc_Sex_meta_analysis.tsv', 
                name = 'Sex Normalised, meta-analysis (DLPFC)', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)
res_acc %>%
  tibble::rownames_to_column(var = "gene_id") %>% 
  write.table(file = 'CMC_acc_Sex_meta_analysis.tsv', sep = '\t', row.names=F, quote=F)
nEXP_OBJ = File('CMC_acc_Sex_meta_analysis.tsv', 
                name = 'Sex Normalised, meta-analysis (ACC)', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = Ids, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)
```
